Relationships in the extremes and their influence on competition and coexistence

### 2022-07-10 paper/Paper.Rnw
stopped after methods of G2

%G2
Left- or right-tail associated noise $(b_1,b_2)$, with $b_i$ normally distributed with mean $\mu_i$ and standard deviation 
$\sigma$, was generated as pictured in Fig. \ref{fig:noise}, details in SI section \ref{SI-sect:noise}.
To achieve goal G2 from the Introduction, i.e., to explore using a simple model the relative magnitudes of the contributions 
to coexistence that come from ATAs versus other mechanisms, we plotted the terms $\Delta_i^0$, $\Delta_i^E$, $\Delta_i^C$, 
$\Delta_i^{(E\shp C)}$, $\Delta_i^{[E \nat C]}$ and $\Delta_i^{[EC]}$ [see (\ref{eq:full_decomp})] for the lottery model
against the parameters of the model, $\mu_1$, $\mu_2$, $\sigma$ and $\delta$; and we compared 
values on plots. Some mathematical shortcuts, summarized here, simplified plotting. 
First, we assumed, without loss of generality, that $\mu_1 \leq \mu_2$. To understand coexistence, 
it was then sufficient to decompose the GWR of the weaker competitor, species 1. 
Second, we showed that, for the 
lottery model, none of the components in (\ref{eq:full_decomp}) depends independently on $\mu_1$ and $\mu_2$;
instead they depend only on $\mu_1-\mu_2$ (SI section \ref{SI-sect:math_simplifications}). So we plotted 
against $\mu_1 - \mu_2$. 
Third, we showed that the values of all components in (\ref{eq:full_decomp}) were the same 
for both our left- and right-tail associated noises (SI section \ref{SI-sect:math_simplifications}). So we only generated plots 
for left-tail associated noise. For each combination of $\delta=0.2, 0.4, 0.6, 0.8$
and $\mu_1-\mu_2=0,-0.5,-2,-4$,
we plotted all the components of (\ref{eq:full_decomp}) against $\sigma$. 
%Relative importance of contributions was judged from the 
%plots to assess whether and to what extent ATA effects on coexistence were meaningfully large for the lottery model, compared to 
%the contributions of other mechanisms.
Mathematical simplications for the $\delta=1$ case make it straightforward to see that
coexistence is impossible and that the case is relatively trivial (SI 
section \ref{SI-sect:delta1}), so that case is not plotted.  
The simulation methods of \cite{Ellner_2019} were used to compute the components of (\ref{eq:full_decomp}).
Computationally efficient means of performing these simulations, for the lottery model, are in 
SI section \ref{SI-sect:efficient_computation}.

>>>>

%G2
To achieve goal G2 from the Introduction, 
left- or right-tail associated %noise 
log fecundities $(b_1,b_2)$, with $b_i$ normally distributed with mean $\mu_i$ and standard deviation 
$\sigma$, was generated as pictured in Fig. \ref{fig:noise}, details in SI section \ref{SI-sect:noise}.
%To achieve goal G2 from the Introduction, i.e., to explore using a simple model the relative magnitudes of the contributions 
%to coexistence that come from ATAs versus other mechanisms, 
We then plotted the terms $\Delta_i^0$, $\Delta_i^E$, $\Delta_i^C$, 
$\Delta_i^{(E\shp C)}$, $\Delta_i^{[E \nat C]}$ and $\Delta_i^{[EC]}$ [see (\ref{eq:full_decomp})] for the lottery model
against the parameters of the model, $\mu_1$, $\mu_2$, $\sigma$ and $\delta$. %; and we compared values on plots. 
Some mathematical shortcuts, summarized here, simplified plotting. 
First, we assumed, without loss of generality, that $\mu_1 \leq \mu_2$. To understand coexistence, 
it was then sufficient to decompose the GWR of the weaker competitor, species 1. 
Second, we showed that, for the 
lottery model, none of the components in (\ref{eq:full_decomp}) depends independently on $\mu_1$ and $\mu_2$;
instead they depend only on $\mu_1-\mu_2$ (SI section \ref{SI-sect:math_simplifications}). 
So we plotted 
the terms
against $\mu_1 - \mu_2$. 
Third, we showed that the values of all components in (\ref{eq:full_decomp}) were the same 
for both our left- and right-tail associated cases (SI section \ref{SI-sect:math_simplifications}), 
so we only generated plots for left-tail associated noise. 
For each combination of $\delta=0.2, 0.4, 0.6$
and $\mu_1-\mu_2=0,-0.5,-1$,
we plotted all the components of (\ref{eq:full_decomp}) against $\sigma$. 
%Relative importance of contributions was judged from the 
%plots to assess whether and to what extent ATA effects on coexistence were meaningfully large for the lottery model, compared to 
%the contributions of other mechanisms.
Mathematical simplications for the $\delta=1$ case make it straightforward to see that
coexistence is impossible and that the case is relatively trivial (SI 
section \ref{SI-sect:delta1}), so that case is not plotted.  
The simulation methods of \cite{Ellner_2019} were used to compute the components of (\ref{eq:full_decomp}).
Computationally efficient means of performing these simulations, for the lottery model, are in 
SI section \ref{SI-sect:efficient_computation}.
